---
title: "WEARABLE DEVICE VALIDITY ACROSS AGE, SEX AND BMI GROUPS"
author: "Sumayyah Musa"
date: "3/12/2021"
output: 
    html_document:
      df_print: kable
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, echo = TRUE, cache.lazy = FALSE, warning = FALSE, message = FALSE, rows.print = 150)

library(rstatix)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(sjPlot)
library(ggpubr)
library(pastecs)
library(car)
library(lme4)
library(ggbeeswarm)
library(mitml)
```


```{r}
df <- read_csv("wearable_review_data_validity.csv")
head(df)
```

```{r}
summary(df$MAPE)
```


## Data Cleaning 

```{r}
data <- df %>% 
    select(Author, Year, Brand, device_name, device_year, location, Measured, Setting, Wear_Location, age, age_code, 
           BMI, population_n, population_m, population_f, MPE, MAPE)
glimpse(data)
```


### MAPE - missing values

```{r}
data$MAPE <- abs(data$MPE * 100)
summary(data$MAPE)
```


```{r}
data$population_f <- as.numeric(data$population_f)
data$population_m <- as.numeric(data$population_m)
data$BMI <- as.numeric(data$BMI)
data$age <- as.numeric(data$age)
data$population_n <- as.numeric(data$population_n)
```


```{r}
data <- data %>% mutate_if(is.character, as.factor) %>% drop_na(MAPE)

str(data)
```

294 observations removed because of missing data on MAPE.

## Data Cleaning by Variable

```{r}
summary(data)
```


```{r}
ggplot(data, aes(MAPE)) + 
  geom_histogram(bins = 25) +
  theme_classic(base_size = 12)
```

```{r}
ggplot(data, aes(MAPE)) + 
                geom_boxplot() +
                coord_flip() +
                theme_classic(base_size = 12)
```

### Outlier Analysis

#### Run

```{r}
data_no_outliers <- filter(data, MAPE < 200) #1672 before outlier removal
glimpse(data_no_outliers)
```

4 cases removed for having MAPE percent greater than 200%

```{r}
ggplot(data_no_outliers, aes(MAPE)) + 
                  geom_histogram(bins = 30) +
                  theme_classic()
```

```{r}
ggplot(data_no_outliers, aes(MAPE)) + 
                  geom_boxplot() +
                  coord_flip() +
                  theme_classic()
```

### AGE

```{r}
table(data_no_outliers$age_code)

levels(data_no_outliers$age_code) <- c("Adults", "Children", "Older Adults")
levels(data_no_outliers$age_code)
```

### SEX

```{r}
data_no_outliers <- data_no_outliers %>%
        mutate(man_pre = population_m - population_f
        )

data_no_outliers <- data_no_outliers %>%
        mutate(sex = case_when(
                population_m > population_f ~ "Men",
                population_m < population_f ~ "Women"
        ))

data_no_outliers <- data_no_outliers %>%
        mutate(sex_10 = case_when(
                man_pre > -10 & man_pre < 10 ~ "Even",
                man_pre >= 10 ~ "Men",
                man_pre <= -10 ~ "Women"
        ))

table(data_no_outliers$sex_10)

data_no_outliers$sex_10 <- fct_relevel(data_no_outliers$sex_10, c("Women","Even","Men"))
```

```{r}
data_no_outliers$sex <- as.factor(data_no_outliers$sex)
data_no_outliers$sex_10 <- as.factor(data_no_outliers$sex_10)
```

### BMI

```{r}
data_no_outliers <- data_no_outliers %>%
        mutate(bmi_code = case_when(
                BMI >= 18.5 & BMI <= 24.9 ~ "Healthy weight",
                BMI > 24.9 & BMI <= 29.9 ~ "Overweight",
                BMI > 29.9 ~ "Obese"
        ))

table(data_no_outliers$BMI, data_no_outliers$bmi_code)
table(data_no_outliers$bmi_code)
```

### Wear Location

```{r}
table(data_no_outliers$Wear_Location)

data_no_outliers <- data_no_outliers %>%
        mutate(wear_loc = case_when(
                Wear_Location == "Wrist" ~ "Wrist",
                Wear_Location == "Waist/Hip" ~ "Hip",
                Wear_Location == "LAF" ~ "Other",
                Wear_Location == "Thigh" ~ "Other",
                Wear_Location == "Torso" ~ "Other",
                Wear_Location == "Upper Arm" ~ "Other"
        ))

table(data_no_outliers$Wear_Location, data_no_outliers$wear_loc)
table(data_no_outliers$wear_loc)
```


```{r}
data_no_outliers$bmi_code <- as.factor(data_no_outliers$bmi_code)
data_no_outliers$bmi_code <- fct_relevel(data_no_outliers$bmi_code, c("Healthy weight","Overweight","Obese"))
```


## MAPE for Step count, heart rate & energy expenditure across different groups

```{r}
#AGE GROUP
data_no_outliers %>%
    group_by(age_code, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#SEX GROUP
data_no_outliers %>%
    group_by(sex, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#BMI GROUP
data_no_outliers %>%
    group_by(bmi_code, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#number of studies for each population and measures
data_no_outliers <- data_no_outliers %>%
    group_by(Measured, bmi_code, sex, age_code) %>%
    mutate(n_studies = n()) 
glimpse(data_no_outliers)
```

## Brand

```{r}
# Filtering out brands with less than 10 comparisons
table(data_no_outliers$Brand)
data_no_outliers <- filter(data_no_outliers, Brand != "Mio" & Brand != "Xiaomi")
```


```{r}
data_no_outliers %>%
    group_by(Brand, bmi_code, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

```{r}
data_no_outliers %>%
    group_by(Brand, age_code, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

```{r}
data_no_outliers %>%
    group_by(Brand, sex, Measured) %>%
    get_summary_stats(MAPE, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

## PLOTS BY Measures

### Filtering the data by Measured

```{r}
val_data_sc <- filter(data_no_outliers, Measured == "SC") 
val_data_hr <- filter(data_no_outliers, Measured == "HR")
val_data_ee <- filter(data_no_outliers, Measured == "EE")
```


### Validity of Step count by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
#options(repr.plot.width = 25, repr.plot.height = 8)
age_sc_plot <- ggplot(data=subset(val_data_sc, !is.na(age_code)), aes(x = age_code, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +
                    #geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Step Count MAPE (%)") +
                    scale_fill_brewer(palette="Accent") +
                    theme_bw() +
                    labs(fill = "Age Group") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_sc_plot)
```

### Validity of step count by Sex

```{r}
sex_sc_plot <- ggplot(data=subset(val_data_sc, !is.na(sex)), aes(x = sex, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +
                    #geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Step Count MAPE (%)") +
                    scale_fill_brewer(palette="Dark2") +
                    theme_bw() +
                    labs(fill = "Gender") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(sex_sc_plot)
```

### Validity of step count by BMI

```{r}
bmi_sc_plot <- ggplot(data=subset(val_data_sc, !is.na(bmi_code)), aes(x = bmi_code, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +                    
                    #geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Step Count MAPE (%)") +
                    scale_fill_brewer(palette="Set1") +
                    theme_bw() +
                    labs(fill = "BMI Category") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(bmi_sc_plot)
```

### Validity of Heart rate by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
age_hr_plot <- ggplot(data=subset(val_data_hr, !is.na(age_code)), aes(x = age_code, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Heart rate MAPE (%)") +
                    scale_fill_brewer(palette="Accent") +
                    theme_bw() +
                    labs(fill = "Age Group") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_hr_plot)
```

### Validity of heart rate by sex

```{r}
sex_hr_plot <- ggplot(data=subset(val_data_hr, !is.na(sex)), aes(x = sex, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Heart rate MAPE (%)") +
                    scale_fill_brewer(palette="Dark2") +
                    theme_bw() +
                    labs(fill = "Gender") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(sex_hr_plot)
```

### Validity of heart rate by BMI

```{r}
bmi_hr_plot <- ggplot(data=subset(val_data_hr, !is.na(bmi_code)), aes(x = bmi_code, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Heart rate MAPE (%)") +
                    scale_fill_brewer(palette="Set1") +
                    theme_bw() +
                    labs(fill = "BMI Category") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(bmi_hr_plot)
```

### Validity of Energy expenditure by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
age_ee_plot <- ggplot(data=subset(val_data_ee, !is.na(age_code)), aes(x = age_code, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Energy expenditure MAPE (%)") +
                    scale_fill_brewer(palette="Accent") +
                    theme_bw() +
                    labs(fill = "Age Group") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_ee_plot)
```

### Validity of energy expenditure by sex

```{r}
sex_ee_plot <- ggplot(data=subset(val_data_ee, !is.na(sex)), aes(x = sex, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Energy expenditure MAPE (%)") +
                    scale_fill_brewer(palette="Dark2") +
                    theme_bw() +
                    labs(fill = "Gender") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_ee_plot)
```

### Validity of energy expenditure by BMI

```{r}
bmi_ee_plot <- ggplot(data=subset(val_data_ee, !is.na(bmi_code)), aes(x = bmi_code, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_beeswarm(alpha = 0.2, dodge.width=0.2, cex=2, na.rm = TRUE) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    ylab("Energy Expenditure MAPE (%)") +
                    scale_fill_brewer(palette="Set1") +
                    theme_bw() +
                    labs(fill = "BMI Category") +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_ee_plot)
```

```{r}
figure1 <- cowplot::plot_grid(age_sc_plot, sex_sc_plot, bmi_sc_plot, age_ee_plot, sex_ee_plot, bmi_ee_plot, age_hr_plot, sex_hr_plot, bmi_hr_plot, labels = c("A1","A2","A3","B1","B2","B3","C1","C2","C3"),label_size = 12)
```

```{r}
ggsave("figure1.png", plot = figure1, width = 16, height = 10)
```

## Regression Analysis

### Create a unique column for each study 

```{r}
val_data_sc$study_n <- str_c(val_data_sc$Author,"_", val_data_sc$Year, "_", val_data_sc$Brand)
val_data_hr$study_n <- str_c(val_data_hr$Author,"_", val_data_hr$Year, "_", val_data_hr$Brand)
val_data_ee$study_n <- str_c(val_data_ee$Author,"_", val_data_ee$Year, "_", val_data_ee$Brand)
```

## Step Count Models

### Step Count validity by Age

```{r}
sc_age_lm <- lm(MAPE ~ age_code + wear_loc, data = val_data_sc)
summary(sc_age_lm)
aov(sc_age_lm)

sc_age_lmer <- lmer(MAPE ~ age_code + wear_loc + (1 | study_n), data = val_data_sc)
summary(sc_age_lmer)
multilevelR2(sc_age_lmer)

tab_model(sc_age_lm, sc_age_lmer)
```

### Step Count validity by BMI

```{r}
sc_bmi_lm <- lm(MAPE ~ bmi_code + wear_loc, data = val_data_sc)
summary(sc_bmi_lm)
aov(sc_bmi_lm)

sc_bmi_lmer <- lmer(MAPE ~ bmi_code + wear_loc + (1 | study_n), data = val_data_sc)
summary(sc_bmi_lmer)
multilevelR2(sc_bmi_lmer)

tab_model(sc_bmi_lm, sc_bmi_lmer)
```

### Step Count validity by sex

```{r}
sc_sex_lm <- lm(MAPE ~ sex + wear_loc, data = val_data_sc)
summary(sc_sex_lm)
aov(sc_sex_lm)

sc_sex_lmer <- lmer(MAPE ~ sex + wear_loc + (1 | study_n), data = val_data_sc)
summary(sc_sex_lmer)
multilevelR2(sc_sex_lmer)

tab_model(sc_sex_lm, sc_sex_lmer)
```

## Energy Expenditure Models

### Energy Expenditure validity by Age

No EE studies on people other than adults.

```{r}
#ee_age_lm <- lm(MAPE ~ age_code + wear_loc, data = val_data_ee)
#summary(ee_age_lm)
#aov(ee_age_lm)

#ee_age_lmer <- lmer(MAPE ~ age_code + wear_loc + (1 | study_n), data = val_data_ee)
#summary(ee_age_lmer)

#tab_model(ee_age_lm, ee_age_lmer)
```

### Energy Expenditure validity by BMI

```{r}
val_data_ee <- filter(val_data_ee, bmi_code != "Obese")

ee_bmi_lm <- lm(MAPE ~ bmi_code + wear_loc, data = val_data_ee)
summary(ee_bmi_lm)
aov(ee_bmi_lm)

ee_bmi_lmer <- lmer(MAPE ~ bmi_code + wear_loc + (1 | study_n), data = val_data_ee)
summary(ee_bmi_lmer)
multilevelR2(ee_bmi_lmer)

tab_model(ee_bmi_lm, ee_bmi_lmer)
```

### Energy Expenditure validity by sex

```{r}
ee_sex_lm <- lm(MAPE ~ sex + wear_loc, data = val_data_ee)
summary(ee_sex_lm)
aov(ee_sex_lm)

ee_sex_lmer <- lmer(MAPE ~ sex + wear_loc + (1 | study_n), data = val_data_ee)
summary(ee_sex_lmer)
multilevelR2(ee_sex_lmer)

tab_model(ee_sex_lm, ee_sex_lmer)
```

## Heart Rate Models

### Heart Rate validity by Age

```{r}
#hr_age_lm <- lm(MAPE ~ age_code, data = val_data_hr)
#summary(hr_age_lm)
#aov(hr_age_lm)

#hr_age_lmer <- lmer(MAPE ~ age_code + (1 | study_n), data = val_data_hr)
#summary(hr_age_lmer)

#tab_model(hr_age_lm, hr_age_lmer)
```

Not run. Only 2 studies with children for heart rate and no studies with older adults. 

### Heart Rate validity by BMI

```{r}
hr_bmi_lm <- lm(MAPE ~ bmi_code, data = val_data_hr)
summary(hr_bmi_lm)
aov(hr_bmi_lm)

hr_bmi_lmer <- lmer(MAPE ~ bmi_code + (1 | study_n), data = val_data_hr)
summary(hr_bmi_lmer)
multilevelR2(hr_bmi_lmer)

tab_model(hr_bmi_lm, hr_bmi_lmer)
```

### Heart Rate validity by sex

```{r}
hr_sex_lm <- lm(MAPE ~ sex, data = val_data_hr)
summary(hr_sex_lm)
aov(hr_sex_lm)

hr_sex_lmer <- lmer(MAPE ~ sex + (1 | study_n), data = val_data_hr)
summary(hr_sex_lmer)
multilevelR2(hr_sex_lmer)

tab_model(hr_sex_lm, hr_sex_lmer)
```

# Gender sensitivity analysis

```{r}
sc_sex_lmer <- lmer(MAPE ~ sex_10 + wear_loc + (1 | study_n), data = val_data_sc)
summary(sc_sex_lmer)
multilevelR2(sc_sex_lmer)

ee_sex_lmer <- lmer(MAPE ~ sex_10 + wear_loc + (1 | study_n), data = val_data_ee)
summary(ee_sex_lmer)
multilevelR2(ee_sex_lmer)

hr_sex_lmer <- lmer(MAPE ~ sex_10 + (1 | study_n), data = val_data_hr)
summary(hr_sex_lmer)
multilevelR2(hr_sex_lmer)

tab_model(sc_sex_lmer, ee_sex_lmer, hr_sex_lmer)
```




## Step Count by Brand and Age

```{r}
age_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_sc_brand)
```

## Step Count by Brand and BMI

```{r}
bmi_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_sc_brand)
```

## Step Count by Brand and Sex

```{r}
sex_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_sc_brand)
```

## Heart Rate by Brand and Age

```{r}
age_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_hr_brand)
```

## Heart rate by Brand and BMI

```{r}
bmi_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_hr_brand)
```

## Heart rate by Brand and Sex

```{r}
sex_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_hr_brand)
```

## Energy Expenditure by Brand and BMI

```{r}
#options(repr.plot.width = 25, repr.plot.height = 8)
bmi_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = MAPE, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_ee_brand)
```

## Energy Expenditure by Brand and Age

```{r}
age_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = MAPE, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_ee_brand)
```

## Energy Expenditure by Brand and Sex

```{r}
sex_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = MAPE, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_ee_brand)
```


## Analysis by Brand

### Filtering the data by Brand

```{r}
#Step count
val_data_sc_apple <- filter(val_data_sc, Brand == "Apple")
val_data_sc_fitbit <- filter(val_data_sc, Brand == "Fitbit")
val_data_sc_garmin <- filter(val_data_sc, Brand == "Garmin")
val_data_sc_misfit <- filter(val_data_sc, Brand == "Misfit")
val_data_sc_polar <- filter(val_data_sc, Brand == "Polar")
val_data_sc_samsung <- filter(val_data_sc, Brand == "Samsung")
val_data_sc_withings <- filter(val_data_sc, Brand == "Withings")

#Heart rate
val_data_hr_apple <- filter(val_data_hr, Brand == "Apple")
val_data_hr_fitbit <- filter(val_data_hr, Brand == "Fitbit")
val_data_hr_garmin <- filter(val_data_hr, Brand == "Garmin")
val_data_hr_misfit <- filter(val_data_hr, Brand == "Misfit")
val_data_hr_polar <- filter(val_data_hr, Brand == "Polar")
val_data_hr_samsung <- filter(val_data_hr, Brand == "Samsung")
val_data_hr_withings <- filter(val_data_hr, Brand == "Withings")

#Energy expenditure
val_data_ee_apple <- filter(val_data_ee, Brand == "Apple")
val_data_ee_fitbit <- filter(val_data_ee, Brand == "Fitbit")
val_data_ee_garmin <- filter(val_data_ee, Brand == "Garmin")
val_data_ee_misfit <- filter(val_data_ee, Brand == "Misfit")
val_data_ee_polar <- filter(val_data_ee, Brand == "Polar")
val_data_ee_samsung <- filter(val_data_ee, Brand == "Samsung")
val_data_ee_withings <- filter(val_data_ee, Brand == "Withings")
```

## Step Count validity by brand, age, sex & bmi

### Apple

```{}
apple_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_apple, offset = n_studies)

apple_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_apple, offset = n_studies)

apple_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_apple, offset = n_studies)

tab_model(apple_sc_reg1, apple_sc_reg2, apple_sc_reg3)
```

### Fitbit

```{}
fitbit_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_fitbit, offset = n_studies)

fitbit_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_fitbit, offset = n_studies)

fitbit_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_fitbit, offset = n_studies)

tab_model(fitbit_sc_reg1, fitbit_sc_reg2, fitbit_sc_reg3)
```

### Garmin

```{}
garmin_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_garmin, offset = n_studies)

garmin_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_garmin, offset = n_studies)

garmin_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_garmin, offset = n_studies)

tab_model(garmin_sc_reg1,garmin_sc_reg2, garmin_sc_reg3)
```

### Misfit

```{}
misfit_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_misfit, offset = n_studies)

#misfit_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_misfit, offset = n_studies)

misfit_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_misfit, offset = n_studies)

tab_model(misfit_sc_reg1, misfit_sc_reg3)
```

### Polar

```{}
#polar_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_polar, offset = n_studies)

#polar_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_polar, offset = n_studies)

polar_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_polar, offset = n_studies)

tab_model(polar_sc_reg3)
```

### Samsung

```{}
samsung_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_samsung, offset = n_studies)

samsung_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_samsung, offset = n_studies)

samsung_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_samsung, offset = n_studies)

tab_model(samsung_sc_reg1, samsung_sc_reg2, samsung_sc_reg3)
```

### Withings

```{}
#withings_sc_reg1 <- lm(MAPE ~ age_code, val_data_sc_withings, offset = n_studies)

#withings_sc_reg2 <- lm(MAPE ~ sex, val_data_sc_withings, offset = n_studies)

withings_sc_reg3 <- lm(MAPE ~ bmi_code, val_data_sc_withings, offset = n_studies)

tab_model(withings_sc_reg3)
```

## Heart Rate validity by brand, age, sex & bmi

### Apple

```{}
#apple_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_apple, offset = n_studies)

apple_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_apple, offset = n_studies)

apple_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_apple, offset = n_studies)

tab_model(apple_hr_reg2, apple_hr_reg3)
```

### Fitbit

```{}
fitbit_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_fitbit, offset = n_studies)

fitbit_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_fitbit, offset = n_studies)

fitbit_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_fitbit, offset = n_studies)

tab_model(fitbit_hr_reg1, fitbit_hr_reg2, fitbit_hr_reg3)
```

### Garmin

```{}
#garmin_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_garmin, offset = n_studies)

garmin_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_garmin, offset = n_studies)

#garmin_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_garmin, offset = n_studies)

tab_model(garmin_hr_reg2)
```

### Misfit

```{}
#misfit_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_misfit, offset = n_studies)

#misfit_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_misfit, offset = n_studies)

#misfit_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_misfit, offset = n_studies)

#tab_model(misfit_hr_reg3)
```

### Polar

```{}
#polar_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_polar, offset = n_studies)

#polar_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_polar, offset = n_studies)

#polar_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_polar, offset = n_studies)

#tab_model(polar_hr_reg1, polar_hr_reg2, polar_hr_reg3)
```

### Samsung

```{}
#samsung_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_samsung, offset = n_studies)

#samsung_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_samsung, offset = n_studies)

#samsung_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_samsung, offset = n_studies)

#tab_model(samsung_hr_reg1, samsung_hr_reg2, samsung_hr_reg3)
```

### Withings

```{}
#withings_hr_reg1 <- lm(MAPE ~ age_code, val_data_hr_withings, offset = n_studies)

#withings_hr_reg2 <- lm(MAPE ~ sex, val_data_hr_withings, offset = n_studies)

#withings_hr_reg3 <- lm(MAPE ~ bmi_code, val_data_hr_withings, offset = n_studies)

#tab_model(withings_sc_reg3)
```

## Energy Expenditure validity by brand, age, sex & bmi

### Apple

```{}
#apple_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_apple, offset = n_studies)

apple_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_apple, offset = n_studies)

apple_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_apple, offset = n_studies)

tab_model(apple_ee_reg2, apple_ee_reg3)
```

### Fitbit

```{}
#fitbit_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_fitbit, offset = n_studies)

fitbit_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_fitbit, offset = n_studies)

fitbit_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_fitbit, offset = n_studies)

tab_model(fitbit_ee_reg2, fitbit_ee_reg3)
```

### Garmin

```{}
#garmin_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_garmin, offset = n_studies)

garmin_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_garmin, offset = n_studies)

garmin_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_garmin, offset = n_studies)

tab_model(garmin_ee_reg2, garmin_ee_reg3)
```

### Misfit

```{}
#misfit_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_misfit, offset = n_studies)

#misfit_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_misfit, offset = n_studies)

#misfit_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_misfit, offset = n_studies)

#tab_model(misfit_ee_reg1, misfit_ee_reg2, misfit_ee_reg3)
```

### Polar

```{}
#polar_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_polar, offset = n_studies)

#polar_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_polar, offset = n_studies)

#polar_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_polar, offset = n_studies)

#tab_model(polar_ee_reg1, polar_ee_reg2)
```

### Samsung

```{}
#samsung_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_samsung, offset = n_studies)

#samsung_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_samsung, offset = n_studies)

#samsung_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_samsung, offset = n_studies)

#tab_model(samsung_ee_reg1, samsung_ee_reg2, samsung_ee_reg3)
```

### Withings

```{}
#withings_ee_reg1 <- lm(MAPE ~ age_code, val_data_ee_withings, offset = n_studies)

#withings_ee_reg2 <- lm(MAPE ~ sex, val_data_ee_withings, offset = n_studies)

#withings_ee_reg3 <- lm(MAPE ~ bmi_code, val_data_ee_withings, offset = n_studies)

#tab_model(withings_ee_reg3)
```







