---
title: "WEARABLE DEVICE VALIDITY ACROSS AGE, SEX AND BMI GROUPS"
author: "Sumayyah Musa"
date: "3/12/2021"
output: 
    html_document:
      df_print: kable
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, rows.print = 150)

library(tidyverse)
library(ggplot2)
library(cowplot)
library(sjPlot)
library(ggpubr)
library(pastecs)
library(rstatix)
library(car)
```


```{r}
df <- read.csv("val_data.csv")
df <- df[,-1]
```


```{r}
summary(df$MPE)
```

## Data Cleaning 

```{r}
data <- df %>%
  select(Author, Year, Brand, device_name, device_year, location, Measured, Setting, Wear_Location, age, age_code, BMI, population_n, population_m, population_f, MPE)
str(data)
```

```{r}
data$age_code <- as.factor(data$age_code)
data$Brand <- as.factor(data$Brand)
data$Measured <- as.factor(data$Measured)
data$Setting <- as.factor(data$Setting)
data$Wear_Location <- as.factor(data$Wear_Location)
data$population_f <- as.numeric(data$population_f)
data$population_m <- as.numeric(data$population_m)
data$BMI <- as.numeric(data$BMI)
data$age <- as.numeric(data$age)
data$population_n <- as.numeric(data$population_n)

str(data)
```

## Data Cleaning by Variable

### MPE (Outcome Variable)

```{r}
#convert to percentage
data <- data %>%
  mutate(mpe_percent = MPE*100)

summary(data)
```


```{r}
mpe_hist <- ggplot(data, aes(mpe_percent)) + 
                  geom_histogram(bins = 25) +
                  theme_classic()
plot(mpe_hist)
```

```{r}
mpe_box <- ggplot(data, aes(mpe_percent)) + 
                geom_boxplot() +
                coord_flip() +
                theme_classic()
plot(mpe_box)
```


```{r}
#creating a dataframe containing the extreme outliers
df_out <- data %>%
  identify_outliers("mpe_percent") %>%
        filter(is.outlier == TRUE)
```


```{r}
#merging the outlier dataframe with our original data
total <- merge(data, df_out, all.x = TRUE)
#renaming those not outliers as FALSE instead of NA
total$is.outlier[is.na(total$is.outlier)] <- FALSE
table(total$is.outlier)
```


```{r}
#subsetting the non-outliers in the data
df <- subset(total, is.outlier != TRUE)
```


```{r}
df <- df[-c(18:19)]
summary(df)
round(stat.desc(df$mpe_percent),2)
```

```{r}
df <- df %>% drop_na(mpe_percent)
```


```{r}
mpe_hist_clean <- ggplot(df, aes(mpe_percent)) + 
                  geom_histogram(bins = 30) +
                  theme_classic()
plot(mpe_hist_clean)
```


```{r}
mpe_box_clean <- ggplot(df, aes(mpe_percent)) + 
                  geom_boxplot() +
                  coord_flip() +
                  theme_classic()

plot(mpe_box_clean)
```

### AGE

```{r}
levels(df$age_code) <- c("Adults", "Children", "Older Adults")
levels(df$age_code)
```


### SEX

```{r}
df <- df %>%
        mutate(sex = case_when(
                population_m > population_f ~ "Male",
                population_m < population_f ~ "Female"
        ))
```

```{r}
df$sex <- as.factor(df$sex)

df_sex <- drop_na(df, sex)
summary(df_sex)
```

### BMI

```{r}
df <- df_sex %>%
        mutate(bmi_code = case_when(
                BMI >= 18.5 & BMI <= 24.9 ~ "Healthy weight",
                BMI > 24.9 & BMI <= 29.9 ~ "Overweight",
                BMI > 29.9 ~ "Obese"
        ))
```


```{r}
df$bmi_code <- as.factor(df$bmi_code)
df <- drop_na(df, bmi_code)
summary(df)
```


```{r}
table(df$location)
```

```{r}
#relevel factors
df$bmi_code <- fct_relevel(df$bmi_code, c("Healthy weight","Overweight","Obese"))
```


## MPE for Step count, heart rate & energy expenditure across different groups


```{r}
#AGE GROUP
df %>%
    group_by(age_code, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#SEX GROUP
df %>%
    group_by(sex, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#BMI GROUP
df %>%
    group_by(bmi_code, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Measured)
```

```{r}
#number of studies for each population and measures
df <- df %>%
  group_by(Measured, bmi_code, sex, age_code) %>%
      mutate(n_studies = n())
```

## Brand

```{r}
# Filtering out brands with less than 10 comparisons
table(df$Brand)
df <- filter(df, Brand != "Mio" & Brand != "Xiaomi")
```


```{r}
df %>%
    group_by(Brand, bmi_code, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

```{r}
df %>%
    group_by(Brand, age_code, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

```{r}
df %>%
    group_by(Brand, sex, Measured) %>%
    get_summary_stats(mpe_percent, type = "mean_sd") %>%
    arrange(Brand, Measured)
```

## PLOTS BY Measures

### Filtering the data by Measured

```{r}
val_data_sc <- filter(df, Measured == "SC")
val_data_hr <- filter(df, Measured == "HR")
val_data_ee <- filter(df, Measured == "EE")
```


### Validity of Step count by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
#options(repr.plot.width = 25, repr.plot.height = 8)
age_sc_plot <- ggplot(val_data_sc, aes(x = 1, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_sc_plot)
```
### Validity of step count by Sex

```{r}
sex_sc_plot <- ggplot(val_data_sc, aes(x = 1, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(sex_sc_plot)
```

### Validity of step count by BMI

```{r}
bmi_sc_plot <- ggplot(val_data_sc, aes(x = 1, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(bmi_sc_plot)
```

### Validity of Heart rate by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
age_hr_plot <- ggplot(val_data_hr, aes(x = 1, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_hr_plot)
```

### Validity of heart rate by sex

```{r}
sex_hr_plot <- ggplot(val_data_hr, aes(x = 1, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(sex_hr_plot)
```

### Validity of heart rate by BMI

```{r}
bmi_hr_plot <- ggplot(val_data_hr, aes(x = 1, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(bmi_hr_plot)
```

### Validity of Energy expenditure by Age

* Dashed grey lines indicate ± 3% measurement error

```{r}
age_ee_plot <- ggplot(val_data_ee, aes(x = 1, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) 
plot(age_ee_plot)
```
### Validity of energy expenditure by sex

```{r}
sex_ee_plot <- ggplot(val_data_ee, aes(x = 1, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) + 
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_ee_plot)
```

### Validity of energy expenditure by BMI

```{r}
bmi_ee_plot <- ggplot(val_data_ee, aes(x =1, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_blank(),
                          axis.title.x = element_blank(),
                          axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_ee_plot)
```

```{r}
figure1 <- cowplot::plot_grid(age_sc_plot, sex_sc_plot, bmi_sc_plot, age_ee_plot, sex_ee_plot, bmi_ee_plot, age_hr_plot, sex_hr_plot, bmi_hr_plot, labels = c("A","A","A","B","B","B","C","C","C"),label_size = 12)
```

```{r}
ggsave("figure1.png", plot = figure1, width = 16, height = 10)
```

## Step Count by Brand and Age

```{r}
age_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_sc_brand)
```

## Step Count by Brand and BMI

```{r}
bmi_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_sc_brand)
```

## Step Count by Brand and Sex

```{r}
sex_sc_brand <- ggplot(val_data_sc, aes(x = Brand, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Step Count MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_sc_brand)
```

## Heart Rate by Brand and Age

```{r}
age_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_hr_brand)
```

## Heart rate by Brand and BMI

```{r}
bmi_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_hr_brand)
```

## Heart rate by Brand and Sex

```{r}
sex_hr_brand <- ggplot(val_data_hr, aes(x = Brand, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Heart Rate MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_hr_brand)
```

## Energy Expenditure by Brand and BMI

```{r}
#options(repr.plot.width = 25, repr.plot.height = 8)
bmi_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = mpe_percent, fill = bmi_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(bmi_ee_brand)
```

## Energy Expenditure by Brand and Age

```{r}
age_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = mpe_percent, fill = age_code)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(age_ee_brand)
```

## Energy Expenditure by Brand and Sex

```{r}
sex_ee_brand <- ggplot(val_data_ee, aes(x = Brand, y = mpe_percent, fill = sex)) +
                    geom_boxplot(na.rm = TRUE) +   
                    geom_hline(yintercept = 3, size = 0.5, colour = "darkslategray", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "darkslategray", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-6, 6)) +
                    ylab("Energy Expenditure MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.ticks.x = element_blank(),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12))
plot(sex_ee_brand)
```

## ANOVA

### Step count validity with Age, Sex & BMI

```{r}
aov_sc_age <- aov(mpe_percent ~ age_code, data = val_data_sc)
summary(aov_sc_age)
```

```{r}
aov_sc_sex <- aov(mpe_percent ~ sex, data = val_data_sc)
summary(aov_sc_sex)
```

```{r}
aov_sc_bmi <- aov(mpe_percent ~ bmi_code, data = val_data_sc)
summary(aov_sc_bmi)
```

### Energy Expenditure validity with Age, Sex & BMI

```{r}
#aov_ee_age <- aov(mpe_percent ~ age_code, data = val_data_ee)
#summary(aov_ee_age)
```

```{r}
aov_ee_sex <- aov(mpe_percent ~ sex, data = val_data_ee)
summary(aov_ee_sex)
```

```{r}
aov_ee_bmi <- aov(mpe_percent ~ bmi_code, data = val_data_ee)
summary(aov_ee_bmi)
```


### Heart Rate validity with Age, Sex & BMI

```{r}
aov_hr_age <- aov(mpe_percent ~ age_code, data = val_data_hr)
summary(aov_hr_age)
```

```{r}
aov_hr_sex <- aov(mpe_percent ~ sex, data = val_data_hr)
summary(aov_hr_sex)
```

```{r}
aov_hr_bmi <- aov(mpe_percent ~ bmi_code, data = val_data_hr)
summary(aov_hr_bmi)
```

## Post Hoc Test

```{r}
tuk_sc_age <- TukeyHSD(aov_sc_age)
tuk_sc_age
```

```{r}
tuk_sc_bmi <- TukeyHSD(aov_sc_bmi)
tuk_sc_bmi
```

```{r}
tuk_ee_bmi <- TukeyHSD(aov_ee_bmi)
tuk_ee_bmi
```

### Grouping measures by wear location

```{r}
df %>%
  group_by(Measured, Wear_Location) %>%
  get_summary_stats(mpe_percent, type = "mean_sd") %>%
  arrange(Measured)
```


## Regression Analysis

### Step Count validity by Age, sex and bmi

```{r}
sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc, offset = n_studies)

sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc, offset = n_studies)

sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc, offset = n_studies)

tab_model(sc_reg1, sc_reg2, sc_reg3)
```

#### With wear location as a covariance

```{r}
sc_wl_reg1 <- lm(mpe_percent ~ age_code + Wear_Location, val_data_sc, offset = n_studies)

sc_wl_reg2 <- lm(mpe_percent ~ sex + Wear_Location, val_data_sc, offset = n_studies)

sc_wl_reg3 <- lm(mpe_percent ~ bmi_code + Wear_Location, val_data_sc, offset = n_studies)

tab_model(sc_wl_reg1, sc_wl_reg2, sc_wl_reg3)
```

### Energy Expenditure validity by age, sex & bmi

```{r}
#ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee, offset = n_studies)

ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee, offset = n_studies)

ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee, offset = n_studies)

tab_model(ee_reg2, ee_reg3)
```

#### With wear location as a covariance

```{r}
#ee_wl_reg1 <- lm(mpe_percent ~ age_code + Wear_Location, val_data_ee, offset = n_studies)

ee_wl_reg2 <- lm(mpe_percent ~ sex + Wear_Location, val_data_ee, offset = n_studies)

ee_wl_reg3 <- lm(mpe_percent ~ bmi_code + Wear_Location, val_data_ee, offset = n_studies)

tab_model(ee_wl_reg2, ee_wl_reg3)
```

### Heart Rate validity by age, sex & bmi

```{r}
hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr, offset = n_studies)

hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr, offset = n_studies)

hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr, offset = n_studies)

tab_model(hr_reg1, hr_reg2, hr_reg3)
```

#### With wear location as a covariance

```{r}
#hr_wl_reg1 <- lm(mpe_percent ~ age_code + Wear_Location, val_data_hr, offset = n_studies)

#hr_wl_reg2 <- lm(mpe_percent ~ sex + Wear_Location, val_data_hr, offset = n_studies)

#hr_wl_reg3 <- lm(mpe_percent ~ bmi_code + Wear_Location, val_data_hr, offset = n_studies)

#tab_model(hr_wl_reg1, hr_wl_reg2, hr_wl_reg3)
```

## Analysis by Brand

### Filtering the data by Brand

```{r}
#Step count
val_data_sc_apple <- filter(val_data_sc, Brand == "Apple")
val_data_sc_fitbit <- filter(val_data_sc, Brand == "Fitbit")
val_data_sc_garmin <- filter(val_data_sc, Brand == "Garmin")
val_data_sc_misfit <- filter(val_data_sc, Brand == "Misfit")
val_data_sc_polar <- filter(val_data_sc, Brand == "Polar")
val_data_sc_samsung <- filter(val_data_sc, Brand == "Samsung")
val_data_sc_withings <- filter(val_data_sc, Brand == "Withings")

#Heart rate
val_data_hr_apple <- filter(val_data_hr, Brand == "Apple")
val_data_hr_fitbit <- filter(val_data_hr, Brand == "Fitbit")
val_data_hr_garmin <- filter(val_data_hr, Brand == "Garmin")
val_data_hr_misfit <- filter(val_data_hr, Brand == "Misfit")
val_data_hr_polar <- filter(val_data_hr, Brand == "Polar")
val_data_hr_samsung <- filter(val_data_hr, Brand == "Samsung")
val_data_hr_withings <- filter(val_data_hr, Brand == "Withings")

#Energy expenditure
val_data_ee_apple <- filter(val_data_ee, Brand == "Apple")
val_data_ee_fitbit <- filter(val_data_ee, Brand == "Fitbit")
val_data_ee_garmin <- filter(val_data_ee, Brand == "Garmin")
val_data_ee_misfit <- filter(val_data_ee, Brand == "Misfit")
val_data_ee_polar <- filter(val_data_ee, Brand == "Polar")
val_data_ee_samsung <- filter(val_data_ee, Brand == "Samsung")
val_data_ee_withings <- filter(val_data_ee, Brand == "Withings")
```

## Step Count validity by brand, age, sex & bmi

### Apple

```{r}
apple_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_apple, offset = n_studies)

apple_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_apple, offset = n_studies)

apple_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_apple, offset = n_studies)

tab_model(apple_sc_reg1, apple_sc_reg2, apple_sc_reg3)
```

### Fitbit

```{r}
fitbit_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_fitbit, offset = n_studies)

fitbit_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_fitbit, offset = n_studies)

fitbit_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_fitbit, offset = n_studies)

tab_model(fitbit_sc_reg1, fitbit_sc_reg2, fitbit_sc_reg3)
```

### Garmin

```{r}
garmin_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_garmin, offset = n_studies)

garmin_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_garmin, offset = n_studies)

garmin_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_garmin, offset = n_studies)

tab_model(garmin_sc_reg1,garmin_sc_reg2, garmin_sc_reg3)
```

### Misfit

```{r}
misfit_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_misfit, offset = n_studies)

#misfit_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_misfit, offset = n_studies)

misfit_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_misfit, offset = n_studies)

tab_model(misfit_sc_reg1, misfit_sc_reg3)
```

### Polar

```{r}
#polar_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_polar, offset = n_studies)

#polar_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_polar, offset = n_studies)

polar_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_polar, offset = n_studies)

tab_model(polar_sc_reg3)
```

### Samsung

```{r}
samsung_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_samsung, offset = n_studies)

samsung_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_samsung, offset = n_studies)

samsung_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_samsung, offset = n_studies)

tab_model(samsung_sc_reg1, samsung_sc_reg2, samsung_sc_reg3)
```

### Withings

```{r}
#withings_sc_reg1 <- lm(mpe_percent ~ age_code, val_data_sc_withings, offset = n_studies)

#withings_sc_reg2 <- lm(mpe_percent ~ sex, val_data_sc_withings, offset = n_studies)

withings_sc_reg3 <- lm(mpe_percent ~ bmi_code, val_data_sc_withings, offset = n_studies)

tab_model(withings_sc_reg3)
```

## Heart Rate validity by brand, age, sex & bmi

### Apple

```{r}
#apple_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_apple, offset = n_studies)

apple_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_apple, offset = n_studies)

apple_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_apple, offset = n_studies)

tab_model(apple_hr_reg2, apple_hr_reg3)
```

### Fitbit

```{r}
fitbit_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_fitbit, offset = n_studies)

fitbit_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_fitbit, offset = n_studies)

fitbit_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_fitbit, offset = n_studies)

tab_model(fitbit_hr_reg1, fitbit_hr_reg2, fitbit_hr_reg3)
```

### Garmin

```{r}
#garmin_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_garmin, offset = n_studies)

garmin_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_garmin, offset = n_studies)

#garmin_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_garmin, offset = n_studies)

tab_model(garmin_hr_reg2)
```

### Misfit

```{r}
#misfit_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_misfit, offset = n_studies)

#misfit_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_misfit, offset = n_studies)

#misfit_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_misfit, offset = n_studies)

#tab_model(misfit_hr_reg3)
```

### Polar

```{r}
#polar_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_polar, offset = n_studies)

#polar_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_polar, offset = n_studies)

#polar_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_polar, offset = n_studies)

#tab_model(polar_hr_reg1, polar_hr_reg2, polar_hr_reg3)
```

### Samsung

```{r}
#samsung_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_samsung, offset = n_studies)

#samsung_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_samsung, offset = n_studies)

#samsung_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_samsung, offset = n_studies)

#tab_model(samsung_hr_reg1, samsung_hr_reg2, samsung_hr_reg3)
```

### Withings

```{r}
#withings_hr_reg1 <- lm(mpe_percent ~ age_code, val_data_hr_withings, offset = n_studies)

#withings_hr_reg2 <- lm(mpe_percent ~ sex, val_data_hr_withings, offset = n_studies)

#withings_hr_reg3 <- lm(mpe_percent ~ bmi_code, val_data_hr_withings, offset = n_studies)

#tab_model(withings_sc_reg3)
```

## Energy Expenditure validity by brand, age, sex & bmi

### Apple

```{r}
#apple_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_apple, offset = n_studies)

apple_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_apple, offset = n_studies)

apple_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_apple, offset = n_studies)

tab_model(apple_ee_reg2, apple_ee_reg3)
```

### Fitbit

```{r}
#fitbit_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_fitbit, offset = n_studies)

fitbit_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_fitbit, offset = n_studies)

fitbit_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_fitbit, offset = n_studies)

tab_model(fitbit_ee_reg2, fitbit_ee_reg3)
```

### Garmin

```{r}
#garmin_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_garmin, offset = n_studies)

garmin_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_garmin, offset = n_studies)

garmin_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_garmin, offset = n_studies)

tab_model(garmin_ee_reg2, garmin_ee_reg3)
```

### Misfit

```{r}
#misfit_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_misfit, offset = n_studies)

#misfit_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_misfit, offset = n_studies)

#misfit_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_misfit, offset = n_studies)

#tab_model(misfit_ee_reg1, misfit_ee_reg2, misfit_ee_reg3)
```

### Polar

```{r}
#polar_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_polar, offset = n_studies)

#polar_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_polar, offset = n_studies)

#polar_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_polar, offset = n_studies)

#tab_model(polar_ee_reg1, polar_ee_reg2)
```

### Samsung

```{r}
#samsung_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_samsung, offset = n_studies)

#samsung_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_samsung, offset = n_studies)

#samsung_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_samsung, offset = n_studies)

#tab_model(samsung_ee_reg1, samsung_ee_reg2, samsung_ee_reg3)
```

### Withings

```{r}
#withings_ee_reg1 <- lm(mpe_percent ~ age_code, val_data_ee_withings, offset = n_studies)

#withings_ee_reg2 <- lm(mpe_percent ~ sex, val_data_ee_withings, offset = n_studies)

#withings_ee_reg3 <- lm(mpe_percent ~ bmi_code, val_data_ee_withings, offset = n_studies)

#tab_model(withings_ee_reg3)
```







