---
title: "WEARABLE DEVICE VALIDITY ACROSS AGE, SEX AND BMI GROUPS"
author: "Sumayyah Musa"
date: "3/12/2021"
output: 
    html_document:
       keep_md: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(cowplot)
library(ggbeeswarm)
library(ggpubr)
library(pastecs)
library(rstatix)
library(car)
```

## Read in and glimpse the data

```{r}
val_data <- read.csv("wearable_review_data_validity_edited.csv")
```

## Data Cleaning 
### Subsetting the data to select Step count

```{r}
data <- subset(val_data, Measured != "EE" & Measured != "HR")

glimpse(data)
```

```{r}
data$X1 <- as.character(data$X1)
data$population_f <- as.numeric(data$population_f)
data$population_m <- as.numeric(data$population_m)
data$BMI <- as.numeric(data$BMI)
data$age <- as.numeric(data$age)
```

## Data Cleaning by Variable

### MPE (Outcome Variable)

```{r}
#convert to percentage
data$MPE <- (data$MPE)*100
summary(data$MPE)
```

```{r}
#removing missing values and renaming our final data as df 
df <- drop_na(data, MPE)
```

```{r}
round(stat.desc(df$MPE),2)
```

```{r}
mpe_hist <- ggplot(df, aes(MPE)) + 
                  geom_histogram(bins = 25) +
                  theme_classic()
                  #facet_wrap(~ age_category)
plot(mpe_hist)
```

```{r}
mpe_box <- ggplot(df, aes(MPE)) + 
                geom_boxplot() +
                coord_flip() +
                theme_classic()
                #facet_wrap(~ age_cat)
plot(mpe_box)
```


```{r}
#creating a dataframe containing the extreme outliers
df_out <- df %>%
  identify_outliers("MPE") %>%
        filter(is.extreme == TRUE)
```


```{r}
#merging the outlier dataframe with our original data
total <- merge(df,df_out, all.x = TRUE)
table(total$is.extreme)
```

```{r}
#renaming those not extreme as FALSE instead of NA
total$is.extreme[is.na(total$is.extreme)] <- FALSE
table(total$is.extreme)
```

```{r}
#subsetting the non-outliers in the data
df_val <- subset(total, is.extreme != TRUE)
```

```{r}
summary(df_val$MPE)
```

```{r}
mpe_hist_clean <- ggplot(df_val, aes(MPE)) + 
                  geom_histogram(bins = 30) +
                  theme_classic()
                  #facet_wrap(~ age_cat)
plot(mpe_hist_clean)
```

The distribution looks better now that the outliers have been removed

```{r}
mpe_box_clean <- ggplot(df_val, aes(MPE)) + 
                  geom_boxplot() +
                  coord_flip() +
                  theme_classic()
                  #facet_wrap(~ age_cat)
plot(mpe_box_clean)
```

### AGE

```{r}
round(stat.desc(df_val$age), digits = 1)

df_val$age_code <- factor(df_val$age_code, c("C","A","OA"), labels = c("Children","Adults","Older Adults"))
```

```{r}
addmargins(table(df_val$age_code)) #frequency table of age, including the total

round(prop.table(table(df_val$age_code))*100, digits = 0) #percentage proportion of each category
sum(is.na(df_val$age_code))
```

### GENDER

```{r}
df_val <- df_val %>%
        mutate(sex = case_when(
                population_m > population_f ~ "Male",
                population_m < population_f ~ "Female"
        ))
```

```{r}
df_val$sex <- as.factor(df_val$sex)
addmargins(table(df_val$sex))
round(prop.table(table(df_val$sex))*100, digits = 0)

sum(is.na(df_val$sex))
df_val_sex <- drop_na(df_val, sex)
```

### BMI

```{r}
round(stat.desc(df_val$BMI), digits = 1)

df_val_sex <- df_val_sex %>%
        mutate(bmi_cat = case_when(
                BMI >= 18.5 & BMI <= 24.9 ~ "Healthy weight",
                BMI > 24.9 & BMI <= 29.9 ~ "Overweight",
                BMI > 29.9 ~ "Obese"
        ))
```

```{r}
addmargins(table(df_val_sex$bmi_cat))
round(prop.table(table(df_val_sex$bmi_cat))*100, digits = 0) #percentage

sum(is.na(df_val_sex$bmi_cat))

df <- drop_na(df_val_sex, bmi_cat)

df <- filter(df, bmi_cat != "Obese")
```

There are not enough data for obese individuals.

### Devices

```{r}
df %>%
        group_by(device_name, Setting) %>%
        summarize(count = n()) %>%
        arrange(desc(count)) %>%
        filter(count > 10)
```

```{r}
df_new <- filter(df, Setting != "Free-Living", device_name == "Fitbit One" | device_name == "Fitbit Flex" | device_name == "Fitbit Zip" | device_name == "Fitbit Charge HR" | device_name == "Garmin Vivofit" | device_name == "Withings Pulse O2" | device_name == "Apple Watch")
```

### Summary statistics by the groups

```{r}
#By age groups
df_new %>%
        group_by(device_name,age_code) %>%
        get_summary_stats(MPE, type = "mean_sd") %>%
        arrange(desc(n))
```

```{r}
#By sex groups
df_new %>%
        group_by(device_name, sex) %>%
        get_summary_stats(MPE, type = "mean_sd") %>%
        arrange(desc(n))
```

```{r}
#by BMI groups
df_new %>%
        group_by(device_name, bmi_cat) %>%
        get_summary_stats(MPE, type = "mean_sd") %>%
        arrange(desc(n))
```

```{r}
#relevel factors
df_new$age_code <- fct_relevel(df_new$age_code, c("Adults","Older Adults"))
df_new$sex <- fct_relevel(df_new$sex, c("Female","Male"))
df_new$bmi_cat <- fct_relevel(df_new$bmi_cat, c("Healthy weight","Overweight"))
```

## PLOTS

### Validity of Step count by Age in Controlled setting

* Dashed grey lines indicate ± 3% measurement error

```{r}
#options(repr.plot.width = 25, repr.plot.height = 8)
df_new_age_plot <- ggplot(df_new, aes(x = device_name, y = MPE, colour = device_name)) +
                    geom_boxplot() +
                    geom_beeswarm(dodge.width = 0.2, cex = 0.2, alpha = 0.08) +   
                    geom_hline(yintercept = 0) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "grey", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "grey", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-10, 10)) +
                    ylab("Step MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_text(colour = "grey20", size = 10, angle = 90, hjust = 0.5, 
                                                     vjust = 0.5),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) +
                    facet_wrap(~ age_code)
plot(df_new_age_plot)
```
### Validity of step count by gender in controlled setting

```{r}
df_new_sex_plot <- ggplot(df_new, aes(x = device_name, y = MPE, colour = device_name)) +
                    geom_boxplot() +
                    geom_beeswarm(dodge.width = 0.2, cex = 0.2, alpha = 0.08) +   
                    geom_hline(yintercept = 0) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "grey", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "grey", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-10, 10)) +
                    ylab("Step MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_text(colour = "grey20", size = 10, angle = 90, hjust = 0.5, 
                                                     vjust = 0.5),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) +
                    facet_wrap(~ sex)
plot(df_new_sex_plot)
```

### Validity of step count by BMI in controlled setting

```{r}
df_new_bmi_plot <- ggplot(df_new, aes(x = device_name, y = MPE, colour = device_name)) +
                    geom_boxplot() +
                    geom_beeswarm(dodge.width = 0.2, cex = 0.2, alpha = 0.08) +   
                    geom_hline(yintercept = 0) +  
                    geom_hline(yintercept = 3, size = 0.5, colour = "grey", linetype = "dashed") + 
                    geom_hline(yintercept = -3, size = 0.5, colour = "grey", linetype = "dashed") +   
                    scale_y_continuous(limits=c(-10, 10)) +
                    ylab("Step MPE (%)") +
                    scale_colour_brewer(palette="Dark2") +
                    theme_bw() +
                    theme(axis.text.x = element_text(colour = "grey20", size = 10, angle = 90, hjust = 0.5, 
                                                     vjust = 0.5),
                        axis.text.y = element_text(colour = "grey20", size = 10),
                        strip.text = element_text(face = "italic"),
                        text = element_text(size = 12)) +
                    facet_wrap(~ bmi_cat)
plot(df_new_bmi_plot)
```

```{r}
figure1 <- plot_grid(df_new_age_plot, df_new_sex_plot, df_new_bmi_plot, labels = c('A','B','C'), label_size = 12)
plot(figure1)
```

```{r}
ggsave("figure1.pdf", plot = figure1, width = 20, height = 16)
```


## Regression Analysis

```{r}
reg1 <- lm(MPE ~ 1, df_new)
reg2 <- lm(MPE ~ age_code, df_new)
reg3 <- lm(MPE ~ age_code + bmi_cat, df_new)
reg4 <- lm(MPE ~ age_code + bmi_cat + sex, df_new)

anova(reg1,reg2,reg3,reg4)
```

```{r}
summary(reg2)
```

```{r}
summary(reg3)
```

```{r}
summary(reg4)
```

```{r}
confint(reg3)
```







